Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-12 tex/paper1/paper1.tex
editing the appendix

Hence, the number of effectively independent pixels time-series must
be calculated.  First, a pair of randomly chosen next-nearest neighbor
pixels are selected from the region.  Next nearest neighbor pixels are
chosen as close physical proximity is most likely to express the
strongest interdependence.  Next, the cross correlation $c(\tau)$
function between two randomly chosen next-nearest neighbor pixels is
calculated.  The cross correlation coefficient measures the linear
dependence of two time series $X(t)$ and $Y(t \pm \tau)$ at different
lags $\tau$.  This is used to define a coefficient of independence
between the neighbors,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  {\bf This
procedure is repeated 10,000 times.  For each value of $\rho$ found,
the effective number of pixels $N_{eff}$ is defined as
values is defined as
\begin{equation}\label{eqn:neff}
\label{eqn:nind}
N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
\end{equation}
The probability density function $p\left(N_{eff}\right)$ is found via
a kernel density estimation technique \cite{???} applied to the
distribution of $N_{eff}$ values found by the procedure above.  The
probability density functions for $N_{eff}$ for each wavelength and
region are shown in Figure \ref{???}.  The estimated probability
density function $p\left(N_{eff}\right)$ is included as a prior in the
posterior.

}
\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt{2\pi\sigma^{2}}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$, $N_{f}$
is the number of Fourier frequencies, and $\sigma_{j}$ is the normal
distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution (except
$N_{eff}$), and are given in Table \ref{tab:priors}.  Each MCMC chain
that was run took 100,000 samples, with burn-in assumed to be at
50,000 samples.  The chain is thinned by taking every fifth element in
the chain, forming the final sample from which the parameter estimates
and their uncertainties are calculated.
\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{parameter} &
\colhead{Model 1 and 2} &
\colhead{Model 2 only} \\
}
\startdata
$\log_{10} A$ & $-4.34 \rightarrow 2.00$  & {\it not applicable} \\
$n$ & $1\rightarrow 6$ & {\it not applicable}  \\
$\log_{10} C$ & $-8.68 \rightarrow 2.00$ & {\it not applicable} \\
$\log_{10} \alpha$  & {\it not applicable}  & $8.68 \rightarrow -1.00$ \\
$\beta$ & {\it not applicable} & $0.1 - 10$ (mHz) \\
$\log_{10}\delta$ & {\it not applicable} & $0.00 \rightarrow 3.00$ \\
\enddata
\end{deluxetable}
The \mFpa\ are assumed to
be normally distributed with a width given by $\sigma_{mean}$ as
calculated above.  A five step fitting process is used to fit Models 1
and 2 to the data, and is described below.

\begin{enumerate}
\item The posterior is formed by multiplying the likelihood (equation
  \ref{eqn:likelihood}) by the priors for $A$, $n$ and $C$ (Table
  \ref{tab:priors}).  The MCMC sampler is run to fit Model 1, assuming
  $\sigma_{j} = \sigma_{original, j}$ the width of the distribution of
  Fourier power at frequency $G(\nu_{j})$.  Since the widths
  $\sigma_{original, j}$ are large it allows the fitting algorithm to
  converge to an approximate fit solution.
\item The posterior is formed by multiplying the likelihood (equation
  \ref{eqn:likelihood}) by the priors for $A$, $n$, $C$ and $N_{eff}$
  (Table \ref{tab:priors}).  The MCMC sampler is run to fit Model 1 with
  $\sigma_{j} = \sigma_{original, j}/sqrt{N_{eff}}$, seeded with
  estimated parameter values from step 1.  This generates a better
  estimate to the parameters of the model fit.  The resulting
  parameter estimates are given by the mean values of marginal
  probability distribution functions, and are the final estimates for
  Model 1.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.  This is done by
  (least-squares) fitting $G(\nu)$ to the positive residuals in the
  frequency range 0.1 - 10 mHz.
\item The MCMC sampler is run to fit Model 1,2 assuming $\sigma_{j} =
  \sigma_{original, j}$, seeded with the mean parameter values of
  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
  step 3.
\item The posterior is formed by multiplying the likelihood (equation
  \ref{eqn:likelihood}) by all the priors in Table \ref{tab:priors}.
  The MCMC sampler is run to fit Model 2 with $\sigma_{j} =
  \sigma_{original, j}/\sqrt{N_{eff}}$, seeded with estimated
  parameter values from step 4.  The resulting parameter estimates are
  given by the mean values of marginal probability distribution
  functions, and are the final estimates for Model 2.
\end{enumerate}
Models are selected using the Akaike and Bayesian Information Criteria
\citep{2007MNRAS.377L..74L}.  Conveniently, these quantities are also
calculated by the PyMC package used to perform the MCMC sampling.  The
68\% credible intervals for the parameters are quoted in Table
\ref{tab:parameters}.  The upper and lower limits to the credible
intervals are found by determining the values beyond which 16\% of the
probability lies in each wing of the marginal distributions.

>>>>

Hence, the number of effectively independent pixels time-series must
be calculated. First, a pair of randomly chosen next-nearest neighbor
pixels are selected from the region.  Next nearest neighbor pixels are
chosen as close physical proximity is most likely to express the
strongest interdependence.  Next, the cross correlation $c(\tau)$
function between two randomly chosen next-nearest neighbor pixels is
calculated.  The cross correlation coefficient measures the linear
dependence of two time series $X(t)$ and $Y(t \pm \tau)$ at different
lag {\bf times $\tau$.  This analysis assumes that the linear
  dependence as measured by the cross-correlation coefficient
  estimates the actual dependence between time-series.}

The cross correlation coefficient is used to define a coefficient of
independence between the neighbors,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  This
procedure is repeated 10,000 times.  For each value of $\rho$ found,
the effective number of pixels $N_{eff}$ is defined as
values is defined as
\begin{equation}\label{eqn:neff}
\label{eqn:nind}
N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
\end{equation}
where $\hat{\rho}$ is the arithmetic mean of the values of $\rho$ found.

\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt{2\pi\sigma^{2}}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$, $N_{f}$
is the number of Fourier frequencies, and $\sigma_{j}$ is the normal
distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution (except
$N_{eff}$), and are given in Table \ref{tab:priors}.  Each MCMC chain
that was run took 100,000 samples, with burn-in assumed to be at
50,000 samples.  The chain is thinned by taking every fifth element in
the chain, forming the final sample from which the parameter estimates
and their uncertainties are calculated.
\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{parameter} &
\colhead{Model 1 and 2} &
\colhead{Model 2 only} \\
}
\startdata
$\log_{10} A$ & $-4.34 \rightarrow 2.00$  & {\it not applicable} \\
$n$ & $1\rightarrow 6$ & {\it not applicable}  \\
$\log_{10} C$ & $-8.68 \rightarrow 2.00$ & {\it not applicable} \\
$\log_{10} \alpha$  & {\it not applicable}  & $8.68 \rightarrow -1.00$ \\
$\beta$ & {\it not applicable} & $0.1 - 10$ (mHz) \\
$\log_{10}\delta$ & {\it not applicable} & $0.00 \rightarrow 3.00$ \\
\enddata
\end{deluxetable}
The \mFpa\ are assumed to
be normally distributed with a width given by $\sigma_{mean}$ as
calculated above.  A five step fitting process is used to fit Models 1
and 2 to the data, and is described below.

\begin{enumerate}
\item The posterior is formed by multiplying the likelihood (equation
  \ref{eqn:likelihood}) by the priors for $A$, $n$ and $C$ (Table
  \ref{tab:priors}).  The MCMC sampler is run to fit Model 1, assuming
  $\sigma_{j} = \sigma_{original, j}$ the width of the distribution of
  Fourier power at frequency $G(\nu_{j})$.  Since the widths
  $\sigma_{original, j}$ are large it allows the fitting algorithm to
  converge to an approximate fit solution.
\item The posterior is formed by multiplying the likelihood (equation
  \ref{eqn:likelihood}) by the priors for $A$, $n$, and $C$
  (Table \ref{tab:priors}).  The MCMC sampler is run to fit Model 1 with
  $\sigma_{j} = \sigma_{original, j}/sqrt{N_{eff}}$, seeded with
  estimated parameter values from step 1.  This generates a better
  estimate to the parameters of the model fit.  The resulting
  parameter estimates are given by the mean values of marginal
  probability distribution functions, and are the final estimates for
  Model 1.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.  This is done by
  (least-squares) fitting $G(\nu)$ to the positive residuals in the
  frequency range 0.1 - 10 mHz.
\item The MCMC sampler is run to fit Model 2 assuming $\sigma_{j} =
  \sigma_{original, j}$, seeded with the mean parameter values of
  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
  step 3.
\item The posterior is formed by multiplying the likelihood (equation
  \ref{eqn:likelihood}) by all the priors for Model 2 (Table \ref{tab:priors}).
  The MCMC sampler is run to fit Model 2 with $\sigma_{j} =
  \sigma_{original, j}/\sqrt{N_{eff}}$, seeded with estimated
  parameter values from step 4.  The resulting parameter estimates are
  given by the mean values of marginal probability distribution
  functions, and are the final estimates for Model 2.
\end{enumerate}
Models are selected using the Akaike Information Criteria
\citep{2007MNRAS.377L..74L}.  Conveniently, these quantities are also
calculated by the PyMC package used to perform the MCMC sampling.  The
68\% credible intervals for the parameters are quoted in Table
\ref{tab:parameters}.  The upper and lower limits to the credible
intervals are found by determining the values beyond which 16\% of the
probability lies in each wing of the marginal distributions.
